COG-ED Manuscript

### 2021-11-05 06_Paper/COG-ED/Manuscript.Rmd
started preparation of pipeline data frames

  # create a new data frame for the data that is being used for reaction time analysis
  # (we cannot exclude trials from the main data frame because the computation of d prime depends on hit-ratios, not reaction time)

@@

>>>>

@@

```{r preprocessing, echo=FALSE, message=FALSE, warning=FALSE}

  # create new data frames for the specification curve analysis
  # the data frame names are a combination of three letters from each of these categories, indicating how they will be preprocessed:
  #
  # RT transformations:
  #   (R) raw/none
  #   (L) log
  #   (I) inverse
  #   (S) square-root
  # RT outlier exclusion:
  #   (N) none
  #   (2) 2 SDs from the mean
  #   (5) 2.5 SDs from the mean
  #   (3) 3 SDs from the mean
  #   (T) 0-200 ms after stimulus onset
  # Post-error trials:
  #   (E) excluded
  #   (N) not excluded
  #
  # Example: the data frame "RT_L3E" has log-transformed RT data with no data points beyond 3 SD from the mean and with no trials that followed misses/false alarms

  # one data frame without transformations is a simple copy of the original data frame
  RT_RNN <- data_nback

  # loop across participants and levels for log, inverse and square-root transform

      # make three more copies of the original data frame as a base
      RT_L <- data_nback
      RT_I <- data_nback
      RT_S <- data_nback

      # create index of rows in which the level changes
      levelindex <- c(1,which(data_nback$level != dplyr::lag(data_nback$level)),nrow(data_nback))

        RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"] <- log10(RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"])
        RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"] <- 1/(RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"])
        RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"] <- sqrt(RT_L[levelindex[i]:(levelindex[i+1]-1),"rt"])
      }
